%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Nigel Kurgan}{}

\position{Postdoctoral Research Fellow}
\address{Novo Nordisk Foundation Center for Basic Metabolic Research}

\email{\href{mailto:nigel.kurgan@sund.ku.dk}{\nolinkurl{nigel.kurgan@sund.ku.dk}}}
\orcid{0000-0002-5011-0297}
\googlescholar{Daqi2XQAAAAJ}
\github{nigelkurgan}
\twitter{nigelkurgan}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June 2023}
    {Nigel Kurgan~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{list-of-publications}{%
\section{List of Publications}\label{list-of-publications}}

\textbf{First Author Publications}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-RN256}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Kurgan, N., Baranowski, B., Stoikos, J., MacNeil, A. J.,
Fajardo, V. A., MacPherson, R. E. K., \& Klentrou, P. (2022).
Characterization of sclerostin's response within white adipose tissue to
an obesogenic diet at rest and in response to acute exercise in male
mice {[}Journal Article{]}. \emph{Front Physiol}, \emph{13}, 1061715.
\url{https://doi.org/10.3389/fphys.2022.1061715}}

\leavevmode\vadjust pre{\hypertarget{ref-RN272}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Kurgan, N., Bott, K. N., Helmeczi, W. E., Roy, B. D.,
Brindle, I. D., Klentrou, P., \& Fajardo, V. A. (2019). Low dose lithium
supplementation activates wnt/β-catenin signalling and increases bone
OPG/RANKL ratio in mice {[}Journal Article{]}. \emph{Biochem Biophys Res
Commun}, \emph{511}(2), 394--397.
\url{https://doi.org/10.1016/j.bbrc.2019.02.066}}

\leavevmode\vadjust pre{\hypertarget{ref-RN260}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Kurgan, N., Islam, H., Matusiak, J. B. L., Baranowski,
B. J., Stoikos, J., Fajardo, V. A., MacPherson, R. E. K., Gurd, B. J.,
\& Klentrou, P. (2022). Subcutaneous adipose tissue sclerostin is
reduced and wnt signaling is enhanced following 4-weeks of sprint
interval training in young men with obesity {[}Journal Article{]}.
\emph{Physiol Rep}, \emph{10}(6), e15232.
\url{https://doi.org/10.14814/phy2.15232}}

\leavevmode\vadjust pre{\hypertarget{ref-RN275}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Kurgan, N., Logan-Sprenger, H., Falk, B., \& Klentrou,
P. (2018). Bone and inflammatory responses to training in female rowers
over an olympic year {[}Journal Article{]}. \emph{Med Sci Sports Exerc},
\emph{50}(9), 1810--1817.
\url{https://doi.org/10.1249/mss.0000000000001640}}

\leavevmode\vadjust pre{\hypertarget{ref-RN265}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Kurgan, N., McKee, K., Calleja, M., Josse, A. R., \&
Klentrou, P. (2020). Cytokines, adipokines, and bone markers at rest and
in response to plyometric exercise in obese vs normal weight adolescent
females {[}Journal Article{]}. \emph{Front Endocrinol (Lausanne)},
\emph{11}, 531926. \url{https://doi.org/10.3389/fendo.2020.531926}}

\leavevmode\vadjust pre{\hypertarget{ref-RN271}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Kurgan, N., Noaman, N., Pergande, M. R., Cologna, S. M.,
Coorssen, J. R., \& Klentrou, P. (2019). Changes to the human serum
proteome in response to high intensity interval exercise: A sequential
top-down proteomic analysis {[}Journal Article{]}. \emph{Front Physiol},
\emph{10}, 362. \url{https://doi.org/10.3389/fphys.2019.00362}}

\leavevmode\vadjust pre{\hypertarget{ref-RN255}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Kurgan, N., Skelly, L. E., Ludwa, I. A., Klentrou, P.,
\& Josse, A. R. (2022). Twelve weeks of a diet and exercise intervention
alters the acute bone response to exercise in adolescent females with
overweight/obesity {[}Journal Article{]}. \emph{Front Physiol},
\emph{13}, 1049604. \url{https://doi.org/10.3389/fphys.2022.1049604}}

\leavevmode\vadjust pre{\hypertarget{ref-RN254}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Kurgan, N., Stoikos, J., Baranowski, B. J., Yumol, J.,
Dhaliwal, R., Sweezey-Munroe, J. B., Fajardo, V. A., Gittings, W.,
Macpherson, R. E. K., \& Klentrou, P. (2023). Sclerostin influences
exercise-induced adaptations in body composition and white adipose
tissue morphology in male mice {[}Journal Article{]}. \emph{J Bone Miner
Res}, \emph{38}(4), 541--555. \url{https://doi.org/10.1002/jbmr.4768}}

\leavevmode\vadjust pre{\hypertarget{ref-RN277}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Kurgan, N., Tsakiridis, E., Kouvelioti, R., Moore, J.,
Klentrou, P., \& Tsiani, E. (2017). Inhibition of human lung cancer cell
proliferation and survival by post-exercise serum is associated with the
inhibition of akt, mTOR, p70 S6K, and Erk1/2 {[}Journal Article{]}.
\emph{Cancers (Basel)}, \emph{9}(5).
\url{https://doi.org/10.3390/cancers9050046}}

\leavevmode\vadjust pre{\hypertarget{ref-RN270}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Kurgan, N., Whitley, K. C., Maddalena, L. A., Moradi,
F., Stoikos, J., Hamstra, S. I., Rubie, E. A., Kumar, M., Roy, B. D.,
Woodgett, J. R., Stuart, J. A., \& Fajardo, V. A. (2019). A
low-therapeutic dose of lithium inhibits GSK3 and enhances myoblast
fusion in C2C12 cells {[}Journal Article{]}. \emph{Cells}, \emph{8}(11).
\url{https://doi.org/10.3390/cells8111340}}

\textbf{Co-Author Publications}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-RN253}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Baranowski, R. W., Braun, J. L., Hockey, B. L., Yumol,
J. L., Geromella, M. S., Watson, C. J. F., Kurgan, N., Messner, H. N.,
Whitley, K. C., MacNeil, A. J., Gauquelin-Koch, G., Bertile, F.,
Gittings, W., Vandenboom, R., Ward, W. E., \& Fajardo, V. A. (2023).
Towards countering muscle and bone loss with spaceflight: GSK3 as a
potential target {[}Journal Article{]}. \emph{iScience}, 107047.
https://doi.org/\url{https://doi.org/10.1016/j.isci.2023.107047}}

\leavevmode\vadjust pre{\hypertarget{ref-RN263}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Beigpoor, A., McKinlay, B. J., Kurgan, N., Plyley, M.
J., O'Leary, D., Falk, B., \& Klentrou, P. (2021). Cytokine
concentrations in saliva vs.~Plasma at rest and in response to intense
exercise in adolescent athletes {[}Journal Article{]}. \emph{Ann Hum
Biol}, \emph{48}(5), 389--392.
\url{https://doi.org/10.1080/03014460.2021.1980105}}

\leavevmode\vadjust pre{\hypertarget{ref-RN257}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Copeland, E. N., Watson, C. J. F., Whitley, K. C.,
Baranowski, B. J., Kurgan, N., MacNeil, A. J., MacPherson, R. E. K.,
Fajardo, V. A., \& Allison, D. J. (2022). Kynurenine metabolism is
altered in mdx mice: A potential muscle to brain connection {[}Journal
Article{]}. \emph{Exp Physiol}, \emph{107}(9), 1029--1036.
\url{https://doi.org/10.1113/ep090381}}

\leavevmode\vadjust pre{\hypertarget{ref-RN276}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Dekker, J., Nelson, K., Kurgan, N., Falk, B., Josse, A.,
\& Klentrou, P. (2017). Wnt signaling-related osteokines and
transforming growth factors before and after a single bout of plyometric
exercise in child and adolescent females {[}Journal Article{]}.
\emph{Pediatr Exerc Sci}, \emph{29}(4), 504--512.
\url{https://doi.org/10.1123/pes.2017-0042}}

\leavevmode\vadjust pre{\hypertarget{ref-RN258}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Guzman, A., Kurgan, N., Moniz, S. C., McCarthy, S. F.,
Sale, C., Logan-Sprenger, H., Elliott-Sale, K. J., Hazell, T. J., \&
Klentrou, P. (2022). Menstrual cycle related fluctuations in circulating
markers of bone metabolism at rest and in response to running in
eumenorrheic females {[}Journal Article{]}. \emph{Calcif Tissue Int},
\emph{111}(2), 124--136.
\url{https://doi.org/10.1007/s00223-022-00970-4}}

\leavevmode\vadjust pre{\hypertarget{ref-RN268}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Hamstra, S. I., Kurgan, N., Baranowski, R. W., Qiu, L.,
Watson, C. J. F., Messner, H. N., MacPherson, R. E. K., MacNeil, A. J.,
Roy, B. D., \& Fajardo, V. A. (2020). Low-dose lithium feeding increases
the SERCA2a-to-phospholamban ratio, improving SERCA function in murine
left ventricles {[}Journal Article{]}. \emph{Exp Physiol},
\emph{105}(4), 666--675. \url{https://doi.org/10.1113/ep088061}}

\leavevmode\vadjust pre{\hypertarget{ref-RN267}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Hamstra, S. I., Whitley, K. C., Baranowski, R. W.,
Kurgan, N., Braun, J. L., Messner, H. N., \& Fajardo, V. A. (2020). The
role of phospholamban and GSK3 in regulating rodent cardiac SERCA
function {[}Journal Article{]}. \emph{Am J Physiol Cell Physiol},
\emph{319}(4), C694--c699.
\url{https://doi.org/10.1152/ajpcell.00318.2020}}

\leavevmode\vadjust pre{\hypertarget{ref-RN274}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Klentrou, P., Angrish, K., Awadia, N., Kurgan, N.,
Kouvelioti, R., \& Falk, B. (2018). Wnt signaling-related osteokines at
rest and following plyometric exercise in prepubertal and early pubertal
boys and girls {[}Journal Article{]}. \emph{Pediatr Exerc Sci},
\emph{30}(4), 457--465. \url{https://doi.org/10.1123/pes.2017-0259}}

\leavevmode\vadjust pre{\hypertarget{ref-RN262}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Klentrou, P., McKee, K., McKinlay, B. J., Kurgan, N.,
Roy, B. D., \& Falk, B. (2021). Circulating levels of bone markers after
short-term intense training with increased dairy consumption in
adolescent female athletes {[}Journal Article{]}. \emph{Children
(Basel)}, \emph{8}(11). \url{https://doi.org/10.3390/children8110961}}

\leavevmode\vadjust pre{\hypertarget{ref-RN273}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Kouvelioti, R., Kurgan, N., Falk, B., Ward, W. E.,
Josse, A. R., \& Klentrou, P. (2018). Response of sclerostin and bone
turnover markers to high intensity interval exercise in young women:
Does impact matter? {[}Journal Article{]}. \emph{Biomed Res Int},
\emph{2018}, 4864952. \url{https://doi.org/10.1155/2018/4864952}}

\leavevmode\vadjust pre{\hypertarget{ref-RN269}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Kouvelioti, R., Kurgan, N., Falk, B., Ward, W. E.,
Josse, A. R., \& Klentrou, P. (2019). Cytokine and sclerostin response
to high-intensity interval running versus cycling {[}Journal Article{]}.
\emph{Med Sci Sports Exerc}, \emph{51}(12), 2458--2464.
\url{https://doi.org/10.1249/mss.0000000000002076}}

\leavevmode\vadjust pre{\hypertarget{ref-RN266}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{McKinlay, B. J., Theocharidis, A., Adebero, T., Kurgan,
N., Fajardo, V. A., Roy, B. D., Josse, A. R., H, M. L.-S., Falk, B., \&
Klentrou, P. (2020). Effects of post-exercise whey protein consumption
on recovery indices in adolescent swimmers {[}Journal Article{]}.
\emph{Int J Environ Res Public Health}, \emph{17}(21).
\url{https://doi.org/10.3390/ijerph17217761}}

\leavevmode\vadjust pre{\hypertarget{ref-RN259}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{McKinlay, B. J., Wallace, P. J., Olansky, S., Woods, S.,
Kurgan, N., Roy, B. D., Josse, A. R., Falk, B., \& Klentrou, P. (2022).
Intensified training in adolescent female athletes: A crossover study of
greek yogurt effects on indices of recovery {[}Journal Article{]}.
\emph{J Int Soc Sports Nutr}, \emph{19}(1), 17--33.
\url{https://doi.org/10.1080/15502783.2022.2044732}}

\leavevmode\vadjust pre{\hypertarget{ref-RN261}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Papadopoulos, E., Gillen, J., Moore, D., Au, D., Kurgan,
N., Klentrou, P., Finelli, A., Alibhai, S. M. H., \& Santa Mina, D.
(2021). High-intensity interval training or resistance training versus
usual care in men with prostate cancer on active surveillance: A 3-arm
feasibility randomized controlled trial {[}Journal Article{]}.
\emph{Appl Physiol Nutr Metab}, \emph{46}(12), 1535--1544.
\url{https://doi.org/10.1139/apnm-2021-0365}}

\leavevmode\vadjust pre{\hypertarget{ref-RN264}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Skelly, L. E., Barbour-Tuck, E. N., Kurgan, N., Calleja,
M., Klentrou, P., Falk, B., \& Josse, A. R. (2021). Neutral effect of
increased dairy product intake, as part of a lifestyle modification
program, on cardiometabolic health in adolescent girls with
overweight/obesity: A secondary analysis from a randomized controlled
trial {[}Journal Article{]}. \emph{Front Nutr}, \emph{8}, 673589.
\url{https://doi.org/10.3389/fnut.2021.673589}}


\label{LastPage}~
\end{document}
