---
name: Nigel Kurgan
qualifications: PhD
position: "Postdoctoral Research Fellow"
address: "Novo Nordisk Foundation Center for Basic Metabolic Research"
#profilepic: "./img/headshot.jpg"
#www: cbmr.ku.dk/research/research-groups/deshmukh-group/
email: "nigel.kurgan@sund.ku.dk"
twitter: nigelkurgan
github: nigelkurgan
orcid: "0000-0002-5011-0297"
googlescholar: "Daqi2XQAAAAJ"
aboutme: "Exercise biologist with expertise in metabolism, proteomics, and bioinformatics. I'm interested in combining these approaches to better understand interorgan communication mediated by secreted proteins during exercise and in individuals with metabolic diseases. I am an avid `R` user for data processing, visualization, and communication/reports, and am passionate about open and reproducible science."
headcolor: 414141
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
##Load in oackages
library(tidyverse)
library(here)
library(vitae)
library(kableExtra)
```

```{r functions}
##Load in functions

readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load data, include=FALSE}
##Read in data for CV
readExcelSheets(here::here("data", "nigel_kurgan_cv_data.xlsx"))
```

```{r eval=FALSE, include=FALSE}
# To update CV on a website, here is an example of code to run in the console:
# rmarkdown::render("cv-vitae/cv-vitae.Rmd", output_file = "~/Documents/SR/website-apero/static/files/cv-vitae.pdf")
```

# Current Appointments
```{r}
appointments %>% 
  detailed_entries(what = role,
                   when = glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Education
```{r}
education %>% 
  detailed_entries(what = degree, 
                   when = year, 
                   with = institution, 
                   where = where, 
                   why = details,
                   .protect = FALSE)
```

# Research Experience
```{r}
research %>%
  detailed_entries(what = role,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = institution,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Teaching and Supervision
\footnotesize
*In addition to the formal supervisory roles listed below, I am also actively involved in the supervision and mentorship of junior lab members.*

\normalsize
```{r}
teaching %>%
  detailed_entries(what = institution,
                   when = dates, #glue::glue("{start_date}--{end_date}"),
                   with = role,
                   where = where,
                   why = details,
                   .protect = FALSE)
```

# Leadership, Service and Community Engagement
\footnotesize
*Manuscript peer-review*: Computational and Structural Biotechnology Journal (2), Archives of Physiology and Biochemistry (1), Physiological Reports (1).

\normalsize
```{r}
leadership %>%
  detailed_entries(what = glue::glue("\\textbf{<role>}: <institution> (<where>)",
                                     .open = "<", .close = ">"),
                   why = details,
                   when = dates, #glue::glue("{start_date}--{end_date}"), 
                   .protect = FALSE)

```


# Additional Training and Professional Development
```{r}
training %>%
  detailed_entries(what = glue::glue("\\textbf{<training>} (<institution>)", .open = "<", .close = ">"),
                when = year, 
                .protect = FALSE)

```


# Skills and General Expertise
```{r}
skills %>%
  kable(booktabs = TRUE, format = "latex") %>%
  kable_styling(full_width = F, font_size = 8, latex_options = "hold_position") %>%
  row_spec(0, bold = T)
```


# Awards and Funding
```{r}
awards %>%
  detailed_entries(what = glue::glue("\\textbf{<award>} (<institution>): <details>",
                                     .open = "<", .close = ">"),
                    paste0(year), .protect = FALSE)

```

\newpage
# Publications
**First Author Publications**
```{r}
bibliography_entries(here("data", "first_author.bib")) 
```

**Co-Author Publications**
```{r}
bibliography_entries(here("data", "co_author.bib")) 
```

# Conference Presentations and Published Abstracts
```{r}
conferences %>%
  detailed_entries(glue::glue("\\:<details>", .open = "<", .close = ">"),
                paste0(year, "\\newline~\\newline"), .protect = FALSE)
```

# Guest Lectures
```{r}

presentations <- presentations %>% filter(include == "yes")

presentations %>%
  detailed_entries(glue::glue("\\textbf{<topic>}, <where>: <details>", .open = "<", .close = ">"),
                paste0(year), 
                .protect = FALSE)
```


