%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Nigel Kurgan}{}

\position{Postdoctoral Research Fellow}
\address{Novo Nordisk Foundation Center for Basic Metabolic Research}

\email{\href{mailto:nigel.kurgan@sund.ku.dk}{\nolinkurl{nigel.kurgan@sund.ku.dk}}}
\orcid{0000-0002-5011-0297}
\googlescholar{Daqi2XQAAAAJ}
\github{nigelkurgan}
\twitter{nigelkurgan}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Exercise biologist with expertise in metabolism, proteomics, and
bioinformatics. I'm interested in combining these approaches to better
understand interorgan communication mediated by secreted proteins during
exercise and in individuals with metabolic diseases. I am an avid
\texttt{R} user for data processing, visualization, and
communication/reports, and am passionate about open and reproducible
science.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June 2023}
    {Nigel Kurgan~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{current-appointments}{%
\section{Current Appointments}\label{current-appointments}}

\begin{cventries}
    \cventry{Postdoctoral Research Fellow}{Novo Nordisk Foundation Center for Basic Metabolic Research, University of Copenhagen}{København, Denmark}{Sep 2022--Present}{\begin{cvitems}
\item \href{https://dr.library.brocku.ca/handle/10464/16382}{Functional Proteomics and Metabolism in the Deshmukh Group \faExternalLink}
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Ph.D. Health Biosciences}{Brock University}{St. Catharines, Canada}{2022}{\begin{cvitems}
\item Conferred with Distinction and a Graduate Student Research Excellence Award
\item Funded by Scholarships from NSERC (2017-21) and QEII-GSST (2021-2022)
\item \href{https://dr.library.brocku.ca/handle/10464/16382}{Thesis: Sclerostin influences body composition adaptations to exercise training \faExternalLink}
\end{cvitems}}
    \cventry{M.Sc. Applied Health Sciences}{Brock University}{St. Catharines, Canada}{2017}{\begin{cvitems}
\item Funded by an Ontario Graduate Scholarship
\item \href{https://dr.library.brocku.ca/handle/10464/12927}{Thesis: Physical training, inflammation, and bone integrity in elite female rowers \faExternalLink}
\end{cvitems}}
    \cventry{B.Sc. Biomedical Sciences (Honours)}{Brock University}{St. Catharines, Canada}{2015}{\begin{cvitems}
\item Conferred June 2015 with First-Class Standing
\item Thesis: Mitochondrial function and phospholipid composition changes in mdx mice skeletal muscle
\end{cvitems}}
\end{cventries}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\begin{cventries}
    \cventry{Postdoctoral Fellow}{University of Copenhagen, Novo Nordisk Foundation Center for Basic Metabolic Research}{København, Denmark}{2022-Present}{\begin{cvitems}
\item Studying secretomics and inter-tissue communication with mass spectrometry-based and affinity-based proteomics
\end{cvitems}}
    \cventry{Research Assistant, Coorssen Top-down Proteomics Lab}{Brock University, Department of Biological Sciences}{St. Catharines, Canada}{2017-20}{\begin{cvitems}
\item Top-down proteomic analysis, method development, and teaching
\end{cvitems}}
    \cventry{Research Assistant, Tsiani Cell Signaling Lab}{Brock University, Department of Biological Sciences}{St. Catharines, Canada}{2018-20}{\begin{cvitems}
\item Optimized in vitro assays involving treatment of cancer cells with human serum
\end{cvitems}}
    \cventry{Research Assistant, Department of Kinesiology}{Brock University, The Department of Kinesiology}{}{2015-20}{\begin{cvitems}
\item VO2max and body composition monitoring in diverse populations
\end{cvitems}}
    \cventry{Laboratory Technician, Athlete Monitoring}{Canadian Sports Institute of Ontario}{London, Canada}{2016}{\begin{cvitems}
\item Blood and saliva collection and analysis from professional female athletes
\end{cvitems}}
    \cventry{Research Assistant, Brock-Niagara Center for Health and Well-Being}{Brock University, The Department of Kinesiology}{St. Catharines, Canada}{2011-2015}{\begin{cvitems}
\item Peer support for physical activity in special populations
\end{cvitems}}
    \cventry{Research Assistant, LebLanc Lab}{Brock University, Department of Biological Sciences}{St. Catharines, Canada}{2013-14}{\begin{cvitems}
\item Optimication of mitochondrial isolations and respiration from skeletal muscle of mdx mice
\end{cvitems}}
\end{cventries}

\hypertarget{teaching-and-supervision}{%
\section{Teaching and Supervision}\label{teaching-and-supervision}}

\footnotesize

\emph{In addition to the formal supervisory roles listed below, I am
also actively involved in the supervision and mentorship of junior lab
members.}

\normalsize
\begin{cventries}
    \cventry{University of Copenhagen, NNF CBMR}{Thesis Student Supervision}{København, Denmark}{2023-Present}{\begin{cvitems}
\item Co-supervising an M.Sc. project on exercise-regulated peptides that influence metabolism
\end{cvitems}}
    \cventry{Brock University, Kinesiology}{Thesis Student Supervision}{St. Catharines, Canada}{2017-22}{\begin{cvitems}
\item Co-supervised a M.Sc. project on a bone derived protein that influences muscle fibre type (2020-22)
\item Co-supervised an undergraduate research project on cytokine response to acute exercise (2017-20)
\end{cvitems}}
    \cventry{Brock University, Kinesiology}{Instructor}{St. Catharines, Canada}{2019-20}{\begin{cvitems}
\item KINE 2P09 – Human Physiology (2019-20)
\end{cvitems}}
    \cventry{Brock University, Health Sciences and Kinesiology}{Teaching Assisstant}{St. Catharines, Canada}{2016-21}{\begin{cvitems}
\item KINE 2P09 – Human Physiology (2020-21)
\item KINE 2P97 – Exercise Metabolism (2021)
\item GERO 5P88 – The Process of Aging (2020)
\item KINE 1P98 – Musculoskeletal Anatomy (2018-19)
\item KINE 1P90 – Human Anatomy and Physiology (2017-18)
\item HLSC 1F90 – Introduction to Health Sciences (2016-18)
\end{cvitems}}
    \cventry{Brock University, Biology and Health Sciences}{Laboratory Demonstrator}{St. Catharines, Canada}{2015-20}{\begin{cvitems}
\item AHSC 7P96 – Top-Down Proteomics (2020)
\item HLSC 4P95 – Human Pathology (2016)
\item HLSC 3P02 – Introduction to Human Immunology (2015)
\end{cvitems}}
\end{cventries}

\hypertarget{leadership-service-and-community-engagement}{%
\section{Leadership, Service and Community
Engagement}\label{leadership-service-and-community-engagement}}

\footnotesize

\emph{Manuscript peer-review}: Computational and Structural
Biotechnology Journal (2), Archives of Physiology and Biochemistry (1),
Physiological Reports (1).

\normalsize
\begin{cventries}
    \cventry{\textbf{\href{Conference Planning https://brocku.ca/bone-and-muscle-health/events/mhef-2021/ }{Conference Planning \faExternalLink}}: Brock University's Muscle Health and Education Forum (St. Catharines, Canada)}{}{}{2021}{\begin{cvitems}
\item Designed the program, recruited speakers, and chaired sessions
\end{cvitems}}
    \cventry{\textbf{Conference Symposia Chair}: Brock University's Muscle Health and Education Forum (St. Catharines, Canada)}{}{}{2018-21}{\begin{cvitems}
\item Free Communication chair – Health Science and Biotechnology, Mapping the New Knowledges Meetingx4 years
\end{cvitems}}
    \cventry{\textbf{Conference Symposia Chair}: Ontario Exercise Physiology Conference (Barrie, Canada)}{}{}{2016}{\begin{cvitems}
\item Sessional Chair – Powerhouse Physiology, Ontario Exercise Physiology Conference
\end{cvitems}}
    \cventry{\textbf{Conference Symposia Chair}: Brock University's Muscle Health and Education Forum (St. Catharines, Canada)}{}{}{2015}{\begin{cvitems}
\item Chair and Master of Ceremony – Brock’s Math and Science Undergraduate Research Conference
\end{cvitems}}
    \cventry{\textbf{President of The Math and Science Council}: Brock University, Faculty of Math and Science (St. Catharines, Canada)}{}{}{2011-15}{\begin{cvitems}
\item Co-founded a council that developed mentorship programs and established an annual undergraduate research conference
\end{cvitems}}
\end{cventries}

\hypertarget{additional-training-and-professional-development}{%
\section{Additional Training and Professional
Development}\label{additional-training-and-professional-development}}

\begin{cventries}
    \cventry{\textbf{Course in Laboratory Animal Science EU Function ABD (felasa)} (University of Copenhagen, Department of Experimental Medicine)}{}{}{2023}{}\vspace{-4.0mm}
    \cventry{\textbf{DDA Reproducible Research in R – an advanced workshop on creating collaborative and automated analysis for PhD Students and Postdocs} (Danish Diabetes and Endocrine Academy (DDEA))}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{\textbf{Just Bash It} (University of Copenhagen, Center for Health Data Science)}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{\textbf{From Excel to R} (University of Copenhagen, Center for Health Data Science)}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{\textbf{\href{https://www.linkedin.com/posts/ddeacademy_postdocs-postdoc-research-ugcPost-7008339764479152128-qIHj?utm_source=share&utm_medium=member_desktop}{DDA Postdoc Summit - Challenge \faExternalLink}} (Danish Diabetes and Endocrine Academy (DDEA))}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{\textbf{Canadian Council of Animal Care and Use of Experimental Animals Certification} (Brock University, ACC)}{}{}{2020}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{skills-and-general-expertise}{%
\section{Skills and General
Expertise}\label{skills-and-general-expertise}}

\begin{table}[!h]
\centering\begingroup\fontsize{8}{10}\selectfont

\begin{tabular}{lll}
\toprule
\textbf{Laboratory} & \textbf{Physiological/Technical} & \textbf{Software/Tools}\\
\midrule
Proteomic Technologies & Metabolic Testing (humans and rodents) & R and Rstudio/Rmarkdown\\
Proteomic Sample Preperation (+Robot Automation) & Body Composition (humans and rodents) & Git/Github\\
Extracellular Vesicle Analysis & Phlebotomy & SPSS\\
Secretomics & Mouse Dissection & Delta2D\\
In Vitro Biochemical and Growth Assays & Dietary and Exercise Monitoring & MaxQuant, Perseus, Spectronaut, DIA-NN, MS Fragger\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

\hypertarget{awards-and-funding}{%
\section{Awards and Funding}\label{awards-and-funding}}

\begin{cventries}
    \cventry{\textbf{NSERC Postdoctoral Fellowship} (University of Copenhagen): Awarded 90,000 CAD to study mechanisms of tissue crosstalk mediated by extracellular vesicles}{}{}{2023-25}{}\vspace{-4.0mm}
    \cventry{\textbf{Distinguished Graduate Student} (Brock University): Awarded 100 CAD for being the most distinguished graduate from my graduate program}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{\textbf{CSEP Graduate Student Oral Presentation Finalist} (CSEP Conference): Awarded 250 CAD for being selected as a finalist for best graduate student oral presentation}{}{}{2021}{}\vspace{-4.0mm}
    \cventry{\textbf{QEII Graduate Scholarship in Science and Technology} (Brock University): Awarded a 15,000 CAD scholarship for my Ph.D. work}{}{}{2020-21}{}\vspace{-4.0mm}
    \cventry{\textbf{Jack M Miller Excellence in Research} (Brock University): Awarded 1,341 CAD in recognition of my excellence in research}{}{}{2020}{}\vspace{-4.0mm}
    \cventry{\textbf{NSERC Postgraduate Scholarship – Doctoral} (Brock University): Awarded 63,000 CAD to study bone-secreted proteins during exercise}{}{}{2017-19}{}\vspace{-4.0mm}
    \cventry{\textbf{Dean of Graduate Studies Excellence Scholarship} (Brock University): Awarded 21,000 CAD for my academic excellence}{}{}{2017-19}{}\vspace{-4.0mm}
    \cventry{\textbf{Dean of Graduate Studies Entrance Scholarship – Doctoral} (Brock University): Awarded 2,000 CAD for my academic excellence}{}{}{2017}{}\vspace{-4.0mm}
    \cventry{\textbf{Ontario Graduate Scholarship – Masters} (Brock University): Awarded 15,000 CAD to study bone health in elite female rowers}{}{}{2016-17}{}\vspace{-4.0mm}
    \cventry{\textbf{Dean of Graduate Studies Excellence Scholarship – Masters} (Brock University): Awarded 2,500 CAD for my academic excellence}{}{}{2016-17}{}\vspace{-4.0mm}
    \cventry{\textbf{CSEP Poster Award Finalist} (CSEP Conference): Selected as a finalist for best poster}{}{}{2016}{}\vspace{-4.0mm}
    \cventry{\textbf{Dean of Graduate Studies Spring Research Fellowship} (Brock University): Awarded 4,000 CAD for my academic excellence}{}{}{2016}{}\vspace{-4.0mm}
    \cventry{\textbf{Dean of Graduate Studies Entrance Scholarship} (Brock University): Awarded 2,500 CAD for my academic excellence}{}{}{2015-16}{}\vspace{-4.0mm}
    \cventry{\textbf{Graduate Studies Fellowship} (Brock University): Awarded 7,000 CAD to study the bone response to acute exercise}{}{}{2015}{}\vspace{-4.0mm}
    \cventry{\textbf{Brock Returning Scholars Award/Deans Honour List} (Brock University): Awarded 1,500 CAD for my academic excellence}{}{}{2012-14}{}\vspace{-4.0mm}
    \cventry{\textbf{Brock Entrance Scholars Award} (Brock University): Awarded 2,500 CAD for my academic excellence}{}{}{2010}{}\vspace{-4.0mm}
\end{cventries}

\newpage

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\textbf{First Author Publications}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-RN256}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Kurgan, N., Baranowski, B., Stoikos, J., MacNeil, A. J.,
Fajardo, V. A., MacPherson, R. E. K., \& Klentrou, P. (2022).
Characterization of sclerostin's response within white adipose tissue to
an obesogenic diet at rest and in response to acute exercise in male
mice {[}Journal Article{]}. \emph{Front Physiol}, \emph{13}, 1061715.
\url{https://doi.org/10.3389/fphys.2022.1061715}}

\leavevmode\vadjust pre{\hypertarget{ref-RN272}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Kurgan, N., Bott, K. N., Helmeczi, W. E., Roy, B. D.,
Brindle, I. D., Klentrou, P., \& Fajardo, V. A. (2019). Low dose lithium
supplementation activates wnt/β-catenin signalling and increases bone
OPG/RANKL ratio in mice {[}Journal Article{]}. \emph{Biochem Biophys Res
Commun}, \emph{511}(2), 394--397.
\url{https://doi.org/10.1016/j.bbrc.2019.02.066}}

\leavevmode\vadjust pre{\hypertarget{ref-RN260}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Kurgan, N., Islam, H., Matusiak, J. B. L., Baranowski,
B. J., Stoikos, J., Fajardo, V. A., MacPherson, R. E. K., Gurd, B. J.,
\& Klentrou, P. (2022). Subcutaneous adipose tissue sclerostin is
reduced and wnt signaling is enhanced following 4-weeks of sprint
interval training in young men with obesity {[}Journal Article{]}.
\emph{Physiol Rep}, \emph{10}(6), e15232.
\url{https://doi.org/10.14814/phy2.15232}}

\leavevmode\vadjust pre{\hypertarget{ref-RN275}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Kurgan, N., Logan-Sprenger, H., Falk, B., \& Klentrou,
P. (2018). Bone and inflammatory responses to training in female rowers
over an olympic year {[}Journal Article{]}. \emph{Med Sci Sports Exerc},
\emph{50}(9), 1810--1817.
\url{https://doi.org/10.1249/mss.0000000000001640}}

\leavevmode\vadjust pre{\hypertarget{ref-RN265}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Kurgan, N., McKee, K., Calleja, M., Josse, A. R., \&
Klentrou, P. (2020). Cytokines, adipokines, and bone markers at rest and
in response to plyometric exercise in obese vs normal weight adolescent
females {[}Journal Article{]}. \emph{Front Endocrinol (Lausanne)},
\emph{11}, 531926. \url{https://doi.org/10.3389/fendo.2020.531926}}

\leavevmode\vadjust pre{\hypertarget{ref-RN271}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Kurgan, N., Noaman, N., Pergande, M. R., Cologna, S. M.,
Coorssen, J. R., \& Klentrou, P. (2019). Changes to the human serum
proteome in response to high intensity interval exercise: A sequential
top-down proteomic analysis {[}Journal Article{]}. \emph{Front Physiol},
\emph{10}, 362. \url{https://doi.org/10.3389/fphys.2019.00362}}

\leavevmode\vadjust pre{\hypertarget{ref-RN255}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Kurgan, N., Skelly, L. E., Ludwa, I. A., Klentrou, P.,
\& Josse, A. R. (2022). Twelve weeks of a diet and exercise intervention
alters the acute bone response to exercise in adolescent females with
overweight/obesity {[}Journal Article{]}. \emph{Front Physiol},
\emph{13}, 1049604. \url{https://doi.org/10.3389/fphys.2022.1049604}}

\leavevmode\vadjust pre{\hypertarget{ref-RN254}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Kurgan, N., Stoikos, J., Baranowski, B. J., Yumol, J.,
Dhaliwal, R., Sweezey-Munroe, J. B., Fajardo, V. A., Gittings, W.,
Macpherson, R. E. K., \& Klentrou, P. (2023). Sclerostin influences
exercise-induced adaptations in body composition and white adipose
tissue morphology in male mice {[}Journal Article{]}. \emph{J Bone Miner
Res}, \emph{38}(4), 541--555. \url{https://doi.org/10.1002/jbmr.4768}}

\leavevmode\vadjust pre{\hypertarget{ref-RN277}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Kurgan, N., Tsakiridis, E., Kouvelioti, R., Moore, J.,
Klentrou, P., \& Tsiani, E. (2017). Inhibition of human lung cancer cell
proliferation and survival by post-exercise serum is associated with the
inhibition of akt, mTOR, p70 S6K, and Erk1/2 {[}Journal Article{]}.
\emph{Cancers (Basel)}, \emph{9}(5).
\url{https://doi.org/10.3390/cancers9050046}}

\leavevmode\vadjust pre{\hypertarget{ref-RN270}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Kurgan, N., Whitley, K. C., Maddalena, L. A., Moradi,
F., Stoikos, J., Hamstra, S. I., Rubie, E. A., Kumar, M., Roy, B. D.,
Woodgett, J. R., Stuart, J. A., \& Fajardo, V. A. (2019). A
low-therapeutic dose of lithium inhibits GSK3 and enhances myoblast
fusion in C2C12 cells {[}Journal Article{]}. \emph{Cells}, \emph{8}(11).
\url{https://doi.org/10.3390/cells8111340}}

\textbf{Co-Author Publications}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-RN253}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Baranowski, R. W., Braun, J. L., Hockey, B. L., Yumol,
J. L., Geromella, M. S., Watson, C. J. F., Kurgan, N., Messner, H. N.,
Whitley, K. C., MacNeil, A. J., Gauquelin-Koch, G., Bertile, F.,
Gittings, W., Vandenboom, R., Ward, W. E., \& Fajardo, V. A. (2023).
Towards countering muscle and bone loss with spaceflight: GSK3 as a
potential target {[}Journal Article{]}. \emph{iScience}, 107047.
https://doi.org/\url{https://doi.org/10.1016/j.isci.2023.107047}}

\leavevmode\vadjust pre{\hypertarget{ref-RN263}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Beigpoor, A., McKinlay, B. J., Kurgan, N., Plyley, M.
J., O'Leary, D., Falk, B., \& Klentrou, P. (2021). Cytokine
concentrations in saliva vs.~Plasma at rest and in response to intense
exercise in adolescent athletes {[}Journal Article{]}. \emph{Ann Hum
Biol}, \emph{48}(5), 389--392.
\url{https://doi.org/10.1080/03014460.2021.1980105}}

\leavevmode\vadjust pre{\hypertarget{ref-RN257}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Copeland, E. N., Watson, C. J. F., Whitley, K. C.,
Baranowski, B. J., Kurgan, N., MacNeil, A. J., MacPherson, R. E. K.,
Fajardo, V. A., \& Allison, D. J. (2022). Kynurenine metabolism is
altered in mdx mice: A potential muscle to brain connection {[}Journal
Article{]}. \emph{Exp Physiol}, \emph{107}(9), 1029--1036.
\url{https://doi.org/10.1113/ep090381}}

\leavevmode\vadjust pre{\hypertarget{ref-RN276}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Dekker, J., Nelson, K., Kurgan, N., Falk, B., Josse, A.,
\& Klentrou, P. (2017). Wnt signaling-related osteokines and
transforming growth factors before and after a single bout of plyometric
exercise in child and adolescent females {[}Journal Article{]}.
\emph{Pediatr Exerc Sci}, \emph{29}(4), 504--512.
\url{https://doi.org/10.1123/pes.2017-0042}}

\leavevmode\vadjust pre{\hypertarget{ref-RN258}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Guzman, A., Kurgan, N., Moniz, S. C., McCarthy, S. F.,
Sale, C., Logan-Sprenger, H., Elliott-Sale, K. J., Hazell, T. J., \&
Klentrou, P. (2022). Menstrual cycle related fluctuations in circulating
markers of bone metabolism at rest and in response to running in
eumenorrheic females {[}Journal Article{]}. \emph{Calcif Tissue Int},
\emph{111}(2), 124--136.
\url{https://doi.org/10.1007/s00223-022-00970-4}}

\leavevmode\vadjust pre{\hypertarget{ref-RN268}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Hamstra, S. I., Kurgan, N., Baranowski, R. W., Qiu, L.,
Watson, C. J. F., Messner, H. N., MacPherson, R. E. K., MacNeil, A. J.,
Roy, B. D., \& Fajardo, V. A. (2020). Low-dose lithium feeding increases
the SERCA2a-to-phospholamban ratio, improving SERCA function in murine
left ventricles {[}Journal Article{]}. \emph{Exp Physiol},
\emph{105}(4), 666--675. \url{https://doi.org/10.1113/ep088061}}

\leavevmode\vadjust pre{\hypertarget{ref-RN267}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Hamstra, S. I., Whitley, K. C., Baranowski, R. W.,
Kurgan, N., Braun, J. L., Messner, H. N., \& Fajardo, V. A. (2020). The
role of phospholamban and GSK3 in regulating rodent cardiac SERCA
function {[}Journal Article{]}. \emph{Am J Physiol Cell Physiol},
\emph{319}(4), C694--c699.
\url{https://doi.org/10.1152/ajpcell.00318.2020}}

\leavevmode\vadjust pre{\hypertarget{ref-RN274}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Klentrou, P., Angrish, K., Awadia, N., Kurgan, N.,
Kouvelioti, R., \& Falk, B. (2018). Wnt signaling-related osteokines at
rest and following plyometric exercise in prepubertal and early pubertal
boys and girls {[}Journal Article{]}. \emph{Pediatr Exerc Sci},
\emph{30}(4), 457--465. \url{https://doi.org/10.1123/pes.2017-0259}}

\leavevmode\vadjust pre{\hypertarget{ref-RN262}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Klentrou, P., McKee, K., McKinlay, B. J., Kurgan, N.,
Roy, B. D., \& Falk, B. (2021). Circulating levels of bone markers after
short-term intense training with increased dairy consumption in
adolescent female athletes {[}Journal Article{]}. \emph{Children
(Basel)}, \emph{8}(11). \url{https://doi.org/10.3390/children8110961}}

\leavevmode\vadjust pre{\hypertarget{ref-RN273}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Kouvelioti, R., Kurgan, N., Falk, B., Ward, W. E.,
Josse, A. R., \& Klentrou, P. (2018). Response of sclerostin and bone
turnover markers to high intensity interval exercise in young women:
Does impact matter? {[}Journal Article{]}. \emph{Biomed Res Int},
\emph{2018}, 4864952. \url{https://doi.org/10.1155/2018/4864952}}

\leavevmode\vadjust pre{\hypertarget{ref-RN269}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Kouvelioti, R., Kurgan, N., Falk, B., Ward, W. E.,
Josse, A. R., \& Klentrou, P. (2019). Cytokine and sclerostin response
to high-intensity interval running versus cycling {[}Journal Article{]}.
\emph{Med Sci Sports Exerc}, \emph{51}(12), 2458--2464.
\url{https://doi.org/10.1249/mss.0000000000002076}}

\leavevmode\vadjust pre{\hypertarget{ref-RN266}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{McKinlay, B. J., Theocharidis, A., Adebero, T., Kurgan,
N., Fajardo, V. A., Roy, B. D., Josse, A. R., H, M. L.-S., Falk, B., \&
Klentrou, P. (2020). Effects of post-exercise whey protein consumption
on recovery indices in adolescent swimmers {[}Journal Article{]}.
\emph{Int J Environ Res Public Health}, \emph{17}(21).
\url{https://doi.org/10.3390/ijerph17217761}}

\leavevmode\vadjust pre{\hypertarget{ref-RN259}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{McKinlay, B. J., Wallace, P. J., Olansky, S., Woods, S.,
Kurgan, N., Roy, B. D., Josse, A. R., Falk, B., \& Klentrou, P. (2022).
Intensified training in adolescent female athletes: A crossover study of
greek yogurt effects on indices of recovery {[}Journal Article{]}.
\emph{J Int Soc Sports Nutr}, \emph{19}(1), 17--33.
\url{https://doi.org/10.1080/15502783.2022.2044732}}

\leavevmode\vadjust pre{\hypertarget{ref-RN261}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Papadopoulos, E., Gillen, J., Moore, D., Au, D., Kurgan,
N., Klentrou, P., Finelli, A., Alibhai, S. M. H., \& Santa Mina, D.
(2021). High-intensity interval training or resistance training versus
usual care in men with prostate cancer on active surveillance: A 3-arm
feasibility randomized controlled trial {[}Journal Article{]}.
\emph{Appl Physiol Nutr Metab}, \emph{46}(12), 1535--1544.
\url{https://doi.org/10.1139/apnm-2021-0365}}

\leavevmode\vadjust pre{\hypertarget{ref-RN264}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Skelly, L. E., Barbour-Tuck, E. N., Kurgan, N., Calleja,
M., Klentrou, P., Falk, B., \& Josse, A. R. (2021). Neutral effect of
increased dairy product intake, as part of a lifestyle modification
program, on cardiometabolic health in adolescent girls with
overweight/obesity: A secondary analysis from a randomized controlled
trial {[}Journal Article{]}. \emph{Front Nutr}, \emph{8}, 673589.
\url{https://doi.org/10.3389/fnut.2021.673589}}

\hypertarget{conference-presentations-and-published-abstracts}{%
\section{Conference Presentations and Published
Abstracts}\label{conference-presentations-and-published-abstracts}}

\begin{cventries}
    \cventry{\:\textbf{Kurgan N}, Deshmukh AS. Proposal: Dissecting the role of exercise-induced extracellular vesicles on tissue metabolism. DDA Postdoc Summit, Rønne, Denmark (2022). Poster Presentation.}{}{}{2022\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, Skelly LE, Ludwa LA, Klentrou P, and Josse AR. Do exercise training and dairy consumption influence the acute bone response in adolescent females with overweight/obesity? Proceedings of 18th IBEC – Hosted by York University, Toronto Canada (2022). Poster Presentation.}{}{}{2022\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:Fraschetti EC, Prowting JL, Skelly LE, \textbf{Kurgan N}, Klentrou P, and Josse AR. The Relationship between Inflammatory and Bone Biomarker Responses following Acute High-impact Exercise. Proceedings of 18th IBEC – Hosted by York University, Toronto Canada (2022). Poster Presentation.}{}{}{2022\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, Stoikos J, Baranowski BJ, Dhaliwal R, Sweezey-Munroe JB, Fajardo VA, MacPherson REK, Klentrou P. Sclerostin regulates exercise-induced adaptations in energy expenditure and body composition in C57BL/6J mice. CSEP, Virtual. Proceedings in APNM, 46 (2021). Graduate Student Oral Presentation Award Finalist.}{}{}{2021\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:Prowting JL, Skelly LE, \textbf{Kurgan N}, Klentrou P, and Josse AR. Acute Effects of Milk vs Carbohydrate on Bone Turnover Biomarkers following Exercise in Young Adult Females.  CSEP, Virtual. Proceedings in APNM, 46 (2021). Poster Presentation.}{}{}{2021\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:Klentrou P, Theocharidis A, McKinlay B, Vlachopoulos D, Kouvelioti R, \textbf{Kurgan N}, Falk B. Effects of Post-Exercise Protein Supplementation on Bone Turnover in Adolescent Swimmers.  ECSS (2020). Oral Presentation.}{}{}{2020\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:Barbour-Tuck EN, Skelly LE, \textbf{Kurgan N}, Klentrou P, Josse AR. A lifestyle modification program including higher dairy product intake and exercise is associated with improvements in global cardiometabolic risk in adolescent girls with overweight/obesity. CNS (2020). Poster Presentation.}{}{}{2020\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:Hamstra SI, \textbf{Kurgan N}, Baranowski R, Qiu L, Watson CJF, Messner H, MacNeil AJ, Roy BD, Fajardo VA. Low dose lithium feeding improves murine left ventricular SERCA function by regulating SERCA2a and phospholamban expression. CSEP, Kelowna, Canada, Proceedings in APNM, 44 (2019). Oral Presentation.}{}{}{2019\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, N Noaman, M Pergande, SM Cologna, JR Coorssen, P Klentrou. An anti-inflammatory phenotype following high intensity interval exercise: a sequential top-down proteomic analysis of human serum. Proceedings of ‘Cell’ - Exercise Metabolism Conference, Sitges, Spain (2019). Poster Presentation.}{}{}{2019\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, Maddalena LA, Roy BD, Stuart JA, Fajardo VA. Low therapeutic and sub-therapeutic doses of lithium enhance calcineurin signalling and myoblast fusion in C2C12 cells. CSEP, Niagara Falls, ON.  Proceedings in APNM, 43 (2018). Poster Presentation.}{}{}{2018\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, Noaman N, Coorssen JR, Klentrou P. Sequential top-down analysis of the human serum proteome in response to high intensity exercise and recovery. CSEP, Niagara Falls, ON. Published in APNM, 43 (2018). Oral Presentation.}{}{}{2018\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, B Falk, P Klentrou. Effect of plyometric exercise on Wnt related osteokines in boys and girls. CSEP, Winnipeg, MB. Published in APNM, 42 (2017). Oral Presentation.}{}{}{2018\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, Pepper C. Logan-Sprenger H, Falk B, Klentrou P. Overtraining in elite female endurance sport and bone metabolism. Proceedings of the 2016 Exercise is Medicine Conference. Western University ON, Canada (2016). Oral Presentation.}{}{}{2016\newline~\newline}{}\vspace{-4.0mm}
    \cventry{\:\textbf{Kurgan N}, Logan-Sprenger H, Falk B, Klentrou P. The effect of training for a year on cytokine response and bone health in the Canadian Olympic rowing team. Proceedings of Ontario Exercise Physiology. Barrie ON, Canada (2016). Oral Presentation.}{}{}{2016\newline~\newline}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{guest-lectures}{%
\section{Guest Lectures}\label{guest-lectures}}

\begin{cventries}
    \cventry{\textbf{Basic Metabolic Research and Critical Thinking Ph.D. Seminar}, University of Copenhagen, Center for Protein Research: Lead seminars on the application of mass-spectrometry-based proteomics and metabolomics}{}{}{2023}{}\vspace{-4.0mm}
    \cventry{\textbf{HLSC 4P98 – Leveraging proteomics to understand the molecular response to exercise}, Brock University, Faculty of Biological Sciences: Lectured on top-down vs. bottom-up proteomics and presented my work using top-down proteomics}{}{}{2018-21}{}\vspace{-4.0mm}
    \cventry{\textbf{GERO 5P88 – Molecular mechanisms of age-related bone loss, Annually}, Brock University, Faculty of Applied Health Sciences: Lectured on the importance of bone mass across the lifespan and the temporal mechanisms regulating bone mass}{}{}{2019-20}{}\vspace{-4.0mm}
    \cventry{\textbf{KINE 1P90 – Gas Exchange and Transport, Annually}, Brock University, Faculty of Applied Health Sciences: Gave annual lectures for my supervisors course}{}{}{2017-20}{}\vspace{-4.0mm}
    \cventry{\textbf{KINE 1P90 – The Blood and its Constituents, Annually}, Brock University, Faculty of Applied Health Sciences: Gave annual lectures for my supervisors course}{}{}{2017-20}{}\vspace{-4.0mm}
    \cventry{\textbf{HSLC 2P09 – Ion Channels and Action Potentials, Annually}, Brock University, Faculty of Applied Health Sciences: Gave annual lectures for my supervisors course}{}{}{2017-18}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
